---
title: "R Notebook"
output: html_notebook
---

```{r}
rm(list=ls())

setwd("C:/users/Renske/OneDrive - Erasmus University Rotterdam/Documents/3 hoek")
load("corona.RData")

#install.packages("ggplot2")
library(ggplot2)

#install.packages("namespace", dependencies = T)
library(namespace)

#install.packages("rlang", dependencies = T)
library(rlang)

#install.packages("ggpubr", dependencies = T)
library(ggpubr)

options(max.print=1000000)
#names(corona)

#install.packages("DescTools", dependencies = T)
library(DescTools)

install.packages("multilevelTools")
library(multilevelTools)

library(lmerTest)
```



##Positive encouragement: hugging, kissing, attention etcetera when child does something good
##Simple t-test
```{r}

##mothers have became a bit less encouraging, but not a lot
mean(corona$positiveEncouragement_m_M, na.rm=T)
mean(corona$posencourage_corona_m_M, na.rm=T)
t.test(corona$positiveEncouragement_m_M,corona$posencourage_corona_m_M, paired=T)

##fathers have became a bit less encouraging, but not a lot
mean(corona$positiveEncouragement_m_V, na.rm=T)
mean(corona$posencourage_corona_m_V, na.rm=T)
t.test(corona$positiveEncouragement_m_V,corona$posencourage_corona_m_V, paired=T)

```
##Coerciveness: dwingend: schuldgevoel, schreeuwn, slaan, geiiriteerd
##simple t-tes
```{r}

##mothers have became a tiny bit more coersive, but not significantly 
mean(corona$coerciveparenting_m_M, na.rm=T)
mean(corona$coercive_corona_m_M, na.rm=T)
t.test(corona$coerciveparenting_m_M,corona$coercive_corona_m_M, paired=T)

##fathers have became a tiny bit more coersive, but not significantly 
mean(corona$coerciveparenting_m_V, na.rm=T)
mean(corona$coercive_corona_m_V, na.rm=T)
t.test(corona$coerciveparenting_m_V,corona$coercive_corona_m_V, paired=T)
```
##parent child relation: enjoy hugging, talking, having a good relation
##simple t-test
```{r}

##mothers have became bit less warm in their rela, significntly
mean(corona$parchildrelation_m_M, na.rm=T)
mean(corona$parchildrel_corona_m_M, na.rm=T)
t.test(corona$parchildrelation_m_M,corona$parchildrel_corona_m_M, paired=T)

##fathers have became a tiny bit less warm, not sigificant 
mean(corona$parchildrelation_m_V, na.rm=T)
mean(corona$parchildrel_corona_m_V, na.rm=T)
t.test(corona$parchildrelation_m_V,corona$parchildrel_corona_m_V, paired=T)
```

```{r}
##Make a nice figure for this with only people in both waves WFC
gender<-c("mothers","mothers","fathers","fathers","mothers","mothers","fathers","fathers","mothers","mothers","fathers","fathers")
Parenting<-c("Encouragement", "Encouragement","Encouragement", "Encouragement","Coerciveness", "Coerciveness","Coerciveness", "Coerciveness",
             "Relationship", "Relationship","Relationship", "Relationship")
Wave<-c("wave 1","covid-19 wave", "wave 1", "covid-19 wave","wave 1","covid-19 wave", "wave 1", "covid-19 wave", "wave 1", "covid-19 wave", "wave 1", "covid-19 wave")
selfreportedquality<-c(3.09, 3.07, 3.01,2.97, 1.54, 1.59, 1.53, 1.56, 3.89, 3.81, 3.76, 3.72)
significant<-c("", "","","","+","","","","**","","","")


data1<-data.frame(Parenting, gender, selfreportedquality, significant, Wave)

order_wave<-c("wave 1", "covid-19 wave")
data1$Wave<-factor(data1$Wave, levels=order_wave)

order_gender<-c("mothers", "fathers")
data1$gender<-factor(data1$gender, levels=order_gender)

order_par<-c("Encouragement", "Coerciveness","Relationship" )
data1$Parenting<-factor(data1$Parenting, levels=order_par)

plot<-ggplot(data1, aes(x=Parenting, y=selfreportedquality,group=Wave, fill=Wave ))+
  geom_bar(stat='identity', position='dodge')+
  geom_text(aes(x=Parenting, y=selfreportedquality, label=significant), hjust=-0.2, angle=90)+
  facet_wrap(~gender)+
  labs(y= "Self-reported quality")+
coord_cartesian(ylim = c(1, 4)) +
scale_y_continuous(breaks = c(1:4))+
  theme(axis.text.x = element_text(angle=45, hjust=1))
plot

```

##conclusion: it all decreased a little bit 



###Step3:parenting and werkprive conflict 

##Descriptives

###relation with WFC wave 1 mothers
#Nee
```{r}
cor.test(corona$werkprive_moeder,corona$parchildrelation_m_M)   ##Negative??
cor.test(corona$werkprive_moeder,corona$coerciveparenting_m_M)      ##positive??
cor.test(corona$werkprive_moeder,corona$positiveEncouragement_m_M)  ##negative??
##NO relation before corona

```


##relation with WFC wave 2 mothers 
#werkprive not 
```{r}
cor.test(corona$werkprive_moeder_corona,corona$parchildrel_corona_m_M) 
cor.test(corona$werkprive_moeder_corona,corona$coercive_corona_m_M) 
cor.test(corona$werkprive_moeder_corona,corona$posencourage_corona_m_M) 
#cor.test(corona$werkprive_moeder_corona,corona$consistency_corona_m_M) 
```



##plot this
```{r}
graph1 <- ggplot(corona, aes(x = werkprive_moeder, y = parchildrelation_m_M)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Mothers: Wave 1")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "parent-child rela", x= "work-to-family conflict")+
  scale_x_continuous(limits=c(0,7.2))+ 
  geom_text(x=6.5, y=3.75, label="r= -0.17")

graph2 <- ggplot(corona, aes(x = werkprive_moeder_corona, y = parchildrel_corona_m_M)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Covid-19 wave")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "parent-child rela", x= "work-to-family conflict")+
  scale_x_continuous(limits=c(0,7.2))+ 
  geom_text(x=6.5, y=3.75, label="r= -0.17")


figure <- ggarrange(graph1, graph2,
                    labels = c("", ""),
                    ncol = 1, nrow = 2)
figure
```

```{r}
graph3 <- ggplot(corona, aes(x = werkprive_moeder, y = coerciveparenting_m_M)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Wave 1")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "coercive parenting", x= "work-to-family conflict")+
  scale_x_continuous(limits=c(0,7.2))+
  scale_y_continuous(limits=c(1,2.5))+ 
  geom_text(x=6.5, y=2, label="r= 0.13")

graph4 <- ggplot(corona, aes(x = werkprive_moeder_corona, y = coercive_corona_m_M)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Covid-19 wave")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "coercive parenting", x= "work-to-family conflict")+
  scale_x_continuous(limits=c(0,7.2))+
  scale_y_continuous(limits=c(1,2.5))+ 
  geom_text(x=6.5, y=2, label="r= 0.08")

figure <- ggarrange(graph3, graph4,
                    labels = c("", ""),
                    ncol = 1, nrow = 2)
figure
```


```{r}
graph5 <- ggplot(corona, aes(x = werkprive_moeder, y = positiveEncouragement_m_M)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Wave 1")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "postive encouragement ", x= "work-to-family conflict")+
  scale_x_continuous(limits=c(0,7.2))+
  scale_y_continuous(limits=c(1,4))+ 
  geom_text(x=6.5, y=3.75, label="r= 0.10")

graph6 <- ggplot(corona, aes(x = werkprive_moeder_corona, y = posencourage_corona_m_M)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Covid-19 wave")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "postive encouragement ", x= "work-to-family conflict")+
  scale_x_continuous(limits=c(0,7.2))+
  scale_y_continuous(limits=c(1,4))+ 
  geom_text(x=6.5, y=3.75, label="r= -0.01")


figure <- ggarrange(graph5, graph6,
                    labels = c("", ""),
                    ncol = 1, nrow = 2)
figure

```


```{r}
figure <- ggarrange(graph1, graph3,graph5, graph2,graph4, graph6,
                    labels = c("", ""),
                    ncol = 3, nrow = 2)
figure
```


#Relationship WFC fathers wave 1
#een beetje 
```{r}
cor.test(corona$werkprive_vader,corona$parchildrelation_m_V)   ##Negative??
cor.test(corona$werkprive_vader,corona$coerciveparenting_m_V)      ##positive??
cor.test(corona$werkprive_vader,corona$positiveEncouragement_m_V)  ##negative??
##NO relation before corona
```


##relationship WFC fathers wave 2


```{r}
cor.test(corona$werkprive_vader_corona,corona$parchildrel_corona_m_V) 
cor.test(corona$werkprive_vader_corona,corona$coercive_corona_m_V) 
cor.test(corona$werkprive_vader_corona,corona$posencourage_corona_m_V) 
```



##plot this
```{r}
graph7 <- ggplot(corona, aes(x = werkprive_vader, y = parchildrelation_m_V)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Fathers: Wave 1")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "parent-child rela", x= "work-to-family conflict")+
  scale_x_continuous(limits=c(0,7.2))+ 
  geom_text(x=6.5, y=3.75, label="r= -0.18")

graph8 <- ggplot(corona, aes(x = werkprive_vader_corona, y = parchildrel_corona_m_V)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Covid-19 wave")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "parent-child rela", x= "work-to-family conflict")+
  scale_x_continuous(limits=c(0,7.2))+ 
  geom_text(x=6.5, y=3.75, label="r= -0.47***")


figure <- ggarrange(graph7, graph8,
                    labels = c("", ""),
                    ncol = 1, nrow = 2)
figure
```

```{r}
graph9 <- ggplot(corona, aes(x = werkprive_vader, y = coerciveparenting_m_V)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Wave 1")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "coercive parenting", x= "work-to-family conflict")+
  scale_x_continuous(limits=c(0,7.2))+
  scale_y_continuous(limits=c(1,2.5))+ 
  geom_text(x=6.5, y=2, label="r= 0.11")

graph10 <- ggplot(corona, aes(x = werkprive_vader_corona, y = coercive_corona_m_V)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Covid-19 wave")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "coercive parenting", x= "work-to-family conflict")+
  scale_x_continuous(limits=c(0,7.2))+
  scale_y_continuous(limits=c(1,2.5))+ 
  geom_text(x=6.5, y=2, label="r= 0.22+")

figure <- ggarrange(graph9, graph10,
                    labels = c("", ""),
                    ncol = 1, nrow = 2)
figure
```


```{r}
graph11 <- ggplot(corona, aes(x = werkprive_vader, y = positiveEncouragement_m_V)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Wave 1")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "postive encouragement ", x= "work-to-family conflict")+
  scale_x_continuous(limits=c(0,7.2))+
  scale_y_continuous(limits=c(1,4))+ 
  geom_text(x=6.5, y=3.75, label="r= 0.25*")

graph12 <- ggplot(corona, aes(x = werkprive_vader_corona, y = posencourage_corona_m_V)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Covid-19 wave")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "postive encouragement ", x= "work-to-family conflict")+
  scale_x_continuous(limits=c(0,7.2))+
  scale_y_continuous(limits=c(1,4))+ 
  geom_text(x=6.5, y=3.75, label="r= 0.01")


figure <- ggarrange(graph11, graph12,
                    labels = c("", ""),
                    ncol = 1, nrow = 2)
figure

```

```{r}
figure <- ggarrange(graph7, graph9,graph11, graph8,graph10, graph12,
                    labels = c("", ""),
                    ncol = 3, nrow = 2)
figure

```


#mannen en vrouwen samen? 



######################################################3
###Step3:parenting and privewerk conflict 

##Descriptives

###FWC parenting mothers wave 1
#Nee
```{r}
cor.test(corona$privewerk_moeder,corona$parchildrelation_m_M)   ##Negative??
cor.test(corona$privewerk_moeder,corona$coerciveparenting_m_M)      ##positive??
cor.test(corona$privewerk_moeder,corona$positiveEncouragement_m_M)  ##negative??
##NO relation before corona

```


##FWC mothers wave 2
#yes
```{r}
cor.test(corona$privewerk_moeder_corona,corona$parchildrel_corona_m_M) 
cor.test(corona$privewerk_moeder_corona,corona$coercive_corona_m_M) 
cor.test(corona$privewerk_moeder_corona,corona$posencourage_corona_m_M) 
#cor.test(corona$privewerk_moeder_corona,corona$consistency_corona_m_M) 
```


##plot this

```{r}
graph13 <- ggplot(corona, aes(x = privewerk_moeder, y = parchildrelation_m_M)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Mothers: Wave 1")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "parent-child rela", x= "family-to-work conflict")+
  scale_x_continuous(limits=c(0,7.2))+ 
  geom_text(x=6.5, y=3.75, label="r= -0.36**")

graph14 <- ggplot(corona, aes(x = privewerk_moeder_corona, y = parchildrel_corona_m_M)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Covid-19 wave")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "parent-child rela", x= "family-to-work conflict")+
  scale_x_continuous(limits=c(0,7.2))+ 
  geom_text(x=6.5, y=3.75, label="r= -0.17")


figure <- ggarrange(graph13, graph14,
                    labels = c("", ""),
                    ncol = 1, nrow = 2)
figure
```

```{r}
graph15 <- ggplot(corona, aes(x = privewerk_moeder, y = coerciveparenting_m_M)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Wave 1")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "coercive parenting", x= "family-to-work conflict")+
  scale_x_continuous(limits=c(0,7.2))+
  scale_y_continuous(limits=c(1,2.5))+ 
  geom_text(x=6.5, y=2, label="r= 0.33**")

graph16 <- ggplot(corona, aes(x = privewerk_moeder_corona, y = coercive_corona_m_M)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Covid-19 wave")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "coercive parenting", x= "family-to-work conflict")+
  scale_x_continuous(limits=c(0,7.2))+
  scale_y_continuous(limits=c(1,2.5))+ 
  geom_text(x=6.5, y=2, label="r= 0.30*")

figure <- ggarrange(graph15, graph16,
                    labels = c("", ""),
                    ncol = 1, nrow = 2)
figure
```


```{r}
graph17 <- ggplot(corona, aes(x = privewerk_moeder, y = positiveEncouragement_m_M)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Wave 1")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "postive encouragement ", x= "family-to-work conflict")+
  scale_x_continuous(limits=c(0,7.2))+
  scale_y_continuous(limits=c(1,4))+ 
  geom_text(x=6.5, y=3.75, label="r= -0.01")

graph18 <- ggplot(corona, aes(x = privewerk_moeder_corona, y = posencourage_corona_m_M)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Covid-19 wave")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "postive encouragement ", x= "family-to-work conflict")+
  scale_x_continuous(limits=c(0,7.2))+
  scale_y_continuous(limits=c(1,4))+ 
  geom_text(x=6.5, y=3.75, label="r= -0.05")


figure <- ggarrange(graph17, graph18,
                    labels = c("", ""),
                    ncol = 1, nrow = 2)
figure

```

```{r}
figure <- ggarrange(graph13, graph15,graph17, graph14,graph16, graph18,
                    labels = c("", ""),
                    ncol = 3, nrow = 2)
figure

```


#FWC fathers wave 1
#een beetje 
```{r}
cor.test(corona$privewerk_vader,corona$parchildrelation_m_V)   ##Negative??
cor.test(corona$privewerk_vader,corona$coerciveparenting_m_V)      ##positive??
cor.test(corona$privewerk_vader,corona$positiveEncouragement_m_V)  ##negative??
##NO relation before corona
```


##FWC fathers wave 2


```{r}
cor.test(corona$privewerk_vader_corona,corona$parchildrel_corona_m_V) 
cor.test(corona$privewerk_vader_corona,corona$coercive_corona_m_V) 
cor.test(corona$privewerk_vader_corona,corona$posencourage_corona_m_V) 
#cor.test(corona$privewerk_vader_corona,corona$consistency_corona_m_V) 
```


##plot this

```{r}
graph19 <- ggplot(corona, aes(x = privewerk_vader, y = parchildrelation_m_V)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Fathers: Wave 1")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "parent-child rela", x= "family-to-work conflict")+
  scale_x_continuous(limits=c(0,7.2))+ 
  geom_text(x=6.5, y=3.75, label="r= -0.30**")

graph20 <- ggplot(corona, aes(x = privewerk_vader_corona, y = parchildrel_corona_m_V)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Covid-19 wave")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "parent-child rela", x= "family-to-work conflict")+
  scale_x_continuous(limits=c(0,7.2))+ 
  geom_text(x=6.5, y=3.75, label="r= -0.29**")


figure <- ggarrange(graph19, graph20,
                    labels = c("", ""),
                    ncol = 1, nrow = 2)
figure
```

```{r}
graph21 <- ggplot(corona, aes(x = privewerk_vader, y = coerciveparenting_m_V)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Wave 1")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "coercive parenting", x= "family-to-work conflict")+
  scale_x_continuous(limits=c(0,7.2))+
  scale_y_continuous(limits=c(1,2.5))+ 
  geom_text(x=6.5, y=2, label="r= 0.18")

graph22 <- ggplot(corona, aes(x = privewerk_vader_corona, y = coercive_corona_m_V)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Covid-19 wave")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "coercive parenting", x= "family-to-work conflict")+
  scale_x_continuous(limits=c(0,7.2))+
  scale_y_continuous(limits=c(1,2.5))+ 
  geom_text(x=6.5, y=2, label="r= 0.14")

figure <- ggarrange(graph21, graph22,
                    labels = c("", ""),
                    ncol = 1, nrow = 2)
figure
```


```{r}
graph23 <- ggplot(corona, aes(x = privewerk_vader, y = positiveEncouragement_m_V)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Wave 1")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "postive encouragement ", x= "family-to-work conflict")+
  scale_x_continuous(limits=c(0,7.2))+
  scale_y_continuous(limits=c(1,4))+ 
  geom_text(x=6.5, y=3.75, label="r= -0.07")

graph24 <- ggplot(corona, aes(x = privewerk_vader_corona, y = posencourage_corona_m_V)) +
  geom_jitter(height = 0.02, width = 0.02) +
  ggtitle("Covid-19 wave")+
  geom_smooth(method=lm)+
  theme_bw()+
  labs(y= "postive encouragement ", x= "family-to-work conflict")+
  scale_x_continuous(limits=c(0,7.2))+
  scale_y_continuous(limits=c(1,4))+ 
  geom_text(x=6.5, y=3.75, label="r= -0.06")


figure <- ggarrange(graph23, graph24,
                    labels = c("", ""),
                    ncol = 1, nrow = 2)
figure

```

```{r}
figure <- ggarrange(graph19, graph21,graph23, graph20,graph22, graph24,
                    labels = c("", ""),
                    ncol = 3, nrow = 2)
figure

```




##Three level model of measurements nested within individuals, and individuals nested within households
##http://alexanderdemos.org/Mixed5.html

##Dateframe for mothers
```{r}

##workfamily conflict, family work conflict, education, youngersibling, parenting 123
myvars <- c("Nr_G", "opleidummymoeder", "werkprive_moederm", "privewerk_moederm", "jongerzwoertje","coerciveparenting_M","positiveEncouragement_M","parchildrelation_M")
wave1m <- corona[myvars]

wave1m$ID<-wave1m$Nr_G
wave1m$wave<-"first"
wave1m$opleiding <- wave1m$opleidummymoeder
wave1m$werkprive <- wave1m$werkprive_moederm
wave1m$privewerk <- wave1m$privewerk_moederm
wave1m$jongerzwoertje <- wave1m$jongerzwoertje
wave1m$coersive <- wave1m$coerciveparenting_M
wave1m$encourage <- wave1m$positiveEncouragement_M
wave1m$relation <- wave1m$parchildrelation_M

myvars <- c("ID", "wave","opleiding", "werkprive", "privewerk", "jongerzwoertje","coersive","encourage","relation")
wave1m <- wave1m[myvars]
```



```{r}
##workfamily conflict, family work conflict, education, youngersibling, parenting 123
myvars <- c("Nr_G", "opleidummymoeder", "werkprive_moeder_coronam", "privewerk_moeder_coronam", "jongerzwoertje_corona","coercive_corona_M","posencourage_corona_M","parchildrel_corona_M")
coronawave <- corona[myvars]

coronawave$ID<-coronawave$Nr_G
coronawave$wave<-"corona"
coronawave$opleiding <- coronawave$opleidummymoeder
coronawave$werkprive <- coronawave$werkprive_moeder_coronam
coronawave$privewerk <- coronawave$privewerk_moeder_coronam
coronawave$jongerzwoertje <- coronawave$jongerzwoertje_corona
coronawave$coersive <- coronawave$coercive_corona_M
coronawave$encourage <- coronawave$posencourage_corona_M
coronawave$relation <- coronawave$parchildrel_corona_M

myvars <- c("ID", "wave","opleiding", "werkprive", "privewerk", "jongerzwoertje","coersive","encourage","relation")
coronawave <- coronawave[myvars]

```


```{r}
mothers<-rbind(wave1m, coronawave)
head(mothers)
```
```{r}

##workfamily conflict, family work conflict, education, youngersibling, parenting 123
myvars <- c("Nr_G", "opleidummyvader", "werkprive_vaderm", "privewerk_vaderm", "jongerzwoertje","coerciveparenting_V","positiveEncouragement_V","parchildrelation_V")
wave1v <- corona[myvars]

wave1v$ID<-wave1v$Nr_G
wave1v$wave<-"first"
wave1v$opleiding <- wave1v$opleidummyvader
wave1v$werkprive <- wave1v$werkprive_vaderm
wave1v$privewerk <- wave1v$privewerk_vaderm
wave1v$jongerzwoertje <- wave1v$jongerzwoertje
wave1v$coersive <- wave1v$coerciveparenting_V
wave1v$encourage <- wave1v$positiveEncouragement_V
wave1v$relation <- wave1v$parchildrelation_V

myvars <- c("ID", "wave","opleiding", "werkprive", "privewerk", "jongerzwoertje","coersive","encourage","relation")
wave1v <- wave1v[myvars]
```



```{r}
##workfamily conflict, family work conflict, education, youngersibling, parenting 123
myvars <- c("Nr_G", "opleidummyvader", "werkprive_vader_coronam", "privewerk_vader_coronam", "jongerzwoertje_corona","coercive_corona_V","posencourage_corona_V","parchildrel_corona_V")
coronawavev <- corona[myvars]

coronawavev$ID<-coronawavev$Nr_G
coronawavev$wave<-"corona"
coronawavev$opleiding <- coronawavev$opleidummyvader
coronawavev$werkprive <- coronawavev$werkprive_vader_coronam
coronawavev$privewerk <- coronawavev$privewerk_vader_coronam
coronawavev$jongerzwoertje <- coronawavev$jongerzwoertje_corona
coronawavev$coersive <- coronawavev$coercive_corona_V
coronawavev$encourage <- coronawavev$posencourage_corona_V
coronawavev$relation <- coronawavev$parchildrel_corona_V

myvars <- c("ID", "wave","opleiding", "werkprive", "privewerk", "jongerzwoertje","coersive","encourage","relation")
coronawavev <- coronawavev[myvars]

```


```{r}
fathers<-rbind(wave1v, coronawavev)
```

```{r}
fathers$geslacht<-"father" 
mothers$geslacht<-"mother" 

fathers$inidvidualID<-paste("V",fathers$ID, sep="")
mothers$inidvidualID<-paste("M",mothers$ID, sep="")

parents<-rbind(fathers, mothers)


parents$waver<-parents$wave
parents$waver[parents$wave=="first"]<-"1.first"
parents$waver[parents$wave=="corona"]<-"2.corona"
  table(parents$waver)
```

###positive encouragement
```{r}
wave1vs<-wave1v[-c(21, 80, 71 ),]
coronawavevs<-coronawavev[-c(89,80 ,82 ,93 , 54),]
fatherss<-rbind(wave1vs, coronawavevs)

wave1ms<-wave1m[-c( 34,74 , 77, 16, 56, 57 ),]
coronawaves<-coronawave[-c( 13 ),]
motherss<-rbind(wave1ms, coronawaves)


fatherss$geslacht<-"father" 
motherss$geslacht<-"mother" 

fatherss$inidvidualID<-paste("V",fatherss$ID, sep="")
motherss$inidvidualID<-paste("M",motherss$ID, sep="")

parents<-rbind(fatherss, motherss)


parents$waver<-parents$wave
parents$waver[parents$wave=="first"]<-"1.first"
parents$waver[parents$wave=="corona"]<-"2.corona"
  table(parents$waver)

mmodele0<-lmer(encourage~(1|ID)+ (1|ID:inidvidualID), data=parents)

mmodele1<-lmer(encourage~werkprive+privewerk +waver+ opleiding+ jongerzwoertje +geslacht+ (1|ID)+ (1|ID:inidvidualID), data=parents)
summary(mmodele1)

mmodele2<-lmer(encourage~werkprive*waver+privewerk*waver +opleiding+ jongerzwoertje +geslacht+(1|ID)+ (1|ID:inidvidualID), data=parents)
summary(mmodele2)

#mmodele2<-lmer(encourage~werkprive*wave*geslacht +privewerk*wave*geslacht +opleiding+ jongerzwoertje +(1|ID)+ (1|ID:inidvidualID), data=parents)
#summary(mmodele2)

r.squaredGLMM(mmodele1) 
r.squaredGLMM(mmodele2)
```
###coersive parenting
```{r}

wave1vs<-wave1v[-c(17,71 ,82 ),]
coronawavevs<-coronawavev[-c(96,80 , 17, 54),]
fatherss<-rbind(wave1vs, coronawavevs)

wave1ms<-wave1m[-c(20 ,6 , 70, 56 ),]
coronawaves<-coronawave[-c( 90,20 ),]
motherss<-rbind(wave1ms, coronawaves)


fatherss$geslacht<-"father" 
motherss$geslacht<-"mother" 

fatherss$inidvidualID<-paste("V",fatherss$ID, sep="")
motherss$inidvidualID<-paste("M",motherss$ID, sep="")

parents<-rbind(fatherss, motherss)


parents$waver<-parents$wave
parents$waver[parents$wave=="first"]<-"1.first"
parents$waver[parents$wave=="corona"]<-"2.corona"
  table(parents$waver)

mmodelc0<-lmer(coersive~ (1|ID)+ (1|ID:inidvidualID), data=parents)


mmodelc1<-lmer(coersive~werkprive+privewerk+ waver+opleiding+ jongerzwoertje + geslacht+ (1|ID)+ (1|ID:inidvidualID), data=parents)
summary(mmodelc1)


mmodelc2<-lmer(coersive~werkprive*waver +privewerk*waver +opleiding+ jongerzwoertje + geslacht+ (1|ID)+ (1|ID:inidvidualID), data=parents)
summary(mmodelc2)

#mmodelc2<-lmer(coersive~werkprive*wave*geslacht+ privewerk*wave*geslacht +opleiding+ jongerzwoertje +(1|ID)+ (1|ID:inidvidualID), data=parents)
#summary(mmodelc2)

r.squaredGLMM(mmodelc1) 
r.squaredGLMM(mmodelc2)

```




###Parent child relationship quality
```{r}
wave1vs<-wave1v[-c( 4, 79,92,56  ),]
coronawavevs<-coronawavev[-c( 92, 64, 90),]
motherss<-rbind(wave1vs, coronawavevs)

wave1ms<-wave1m[-c( 21, 10, 91, 7, 71),]
coronawaves<-coronawave[-c(89,80 ,57, 17, 7, 54),]
fatherss<-rbind(wave1ms, coronawaves)

fatherss$geslacht<-"father" 
motherss$geslacht<-"mother" 

fatherss$inidvidualID<-paste("V",fatherss$ID, sep="")
motherss$inidvidualID<-paste("M",motherss$ID, sep="")

parents<-rbind(fatherss, motherss)


parents$waver<-parents$wave
parents$waver[parents$wave=="first"]<-"1.first"
parents$waver[parents$wave=="corona"]<-"2.corona"
  table(parents$waver)

mmodelr0<-lmer(relation~(1|ID)+ (1|ID:inidvidualID), data=parents)

mmodelr1<-lmer(relation~werkprive+privewerk +waver+opleiding+ jongerzwoertje +geslacht+ (1|ID)+ (1|ID:inidvidualID), data=parents)
summary(mmodelr1)

mmodelr2<-lmer(relation~werkprive*waver+privewerk*waver +opleiding+ jongerzwoertje +geslacht+(1|ID)+ (1|ID:inidvidualID), data=parents)
summary(mmodelr2)

#mmodelr2<-lmer(relation~werkprive*wave*geslacht +privewerk*wave*geslacht +opleiding+ jongerzwoertje +(1|ID)+ (1|ID:inidvidualID), data=parents)
#summary(mmodelr2)

r.squaredGLMM(mmodelr1) 
r.squaredGLMM(mmodelr2)
```
###R2 of these multilevel models 
#Pseudo R2
```{r}
install.packages("MuMIn")
library(MuMIn)

r.squaredGLMM(mmodelc0) ###marginal r2, variance explained by fixed effects, there are none, and r2c is conditional r2, variance explained by entire model, including fixed and random effects. This is in the empty model the same as the ICC. 
r.squaredGLMM(mmodelc1) 
r.squaredGLMM(mmodelc2)

r.squaredGLMM(mmodele0) ###marginal r2, variance explained by fixed effects, there are none, and r2c is conditional r2, variance explained by entire model, including fixed and random effects. This is in the empty model the same as the ICC. 
r.squaredGLMM(mmodele1) 
r.squaredGLMM(mmodele2)

r.squaredGLMM(mmodelr0) ###marginal r2, variance explained by fixed effects, there are none, and r2c is conditional r2, variance explained by entire model, including fixed and random effects. This is in the empty model the same as the ICC. 
r.squaredGLMM(mmodelr1) 
r.squaredGLMM(mmodelr2)
```



```{r}
#relationship
1-logLik(mmodelc1)/logLik(mmodelc0)
1-logLik(mmodelc2)/logLik(mmodelc0)

#relationship
1-logLik(mmodele1)/logLik(mmodele0)
1-logLik(mmodele2)/logLik(mmodele0)


#relationship
1-logLik(mmodelr1)/logLik(mmodelr0)
1-logLik(mmodelr2)/logLik(mmodelr0)
```



##reverse wave to see significance for the other wave
```{r}
#parents$geslachtr<-parents$geslacht
#parents$geslachtr[parents$geslacht=="mother"]<-"1.mother"
#parents$geslachtr[parents$geslacht=="father"]<-"2.father"
#  table(parents$geslachtr)
  
parents$waver<-parents$wave
parents$waver[parents$wave=="first"]<-"1.first"
parents$waver[parents$wave=="corona"]<-"2.corona"
  table(parents$waver)
```

```{r}
mmodele2<-lmer(encourage~werkprive*wave+privewerk*wave +opleiding+ jongerzwoertje +geslacht+(1|ID)+ (1|ID:inidvidualID), data=parents)
summary(mmodele2)

mmodelc2<-lmer(coersive~werkprive*wave +privewerk*wave +opleiding+ jongerzwoertje + geslacht+ (1|ID)+ (1|ID:inidvidualID), data=parents)
summary(mmodelc2)

mmodelr2<-lmer(relation~werkprive*wave+privewerk*wave +opleiding+ jongerzwoertje +geslacht+(1|ID)+ (1|ID:inidvidualID), data=parents)
summary(mmodelr2)
```


##With outliers included for comparison 
###positive encouragement
```{r}
wave1vs<-wave1v
coronawavevs<-coronawavev
fatherss<-rbind(wave1vs, coronawavevs)

wave1ms<-wave1m
coronawaves<-coronawave
motherss<-rbind(wave1ms, coronawaves)


fatherss$geslacht<-"father" 
motherss$geslacht<-"mother" 

fatherss$inidvidualID<-paste("V",fatherss$ID, sep="")
motherss$inidvidualID<-paste("M",motherss$ID, sep="")

parents<-rbind(fatherss, motherss)


parents$waver<-parents$wave
parents$waver[parents$wave=="first"]<-"1.first"
parents$waver[parents$wave=="corona"]<-"2.corona"
  table(parents$waver)

mmodele0<-lmer(encourage~(1|ID)+ (1|ID:inidvidualID), data=parents)

mmodele1<-lmer(encourage~werkprive+privewerk +waver+ opleiding+ jongerzwoertje +geslacht+ (1|ID)+ (1|ID:inidvidualID), data=parents)
summary(mmodele1)

mmodele2<-lmer(encourage~werkprive*waver+privewerk*waver +opleiding+ jongerzwoertje +geslacht+(1|ID)+ (1|ID:inidvidualID), data=parents)
summary(mmodele2)

#mmodele2<-lmer(encourage~werkprive*wave*geslacht +privewerk*wave*geslacht +opleiding+ jongerzwoertje +(1|ID)+ (1|ID:inidvidualID), data=parents)
#summary(mmodele2)

r.squaredGLMM(mmodele1) 
r.squaredGLMM(mmodele2)
```
###coersive parenting
```{r}

wave1vs<-wave1v
coronawavevs<-coronawavev
fatherss<-rbind(wave1vs, coronawavevs)

wave1ms<-wave1m
coronawaves<-coronawave
motherss<-rbind(wave1ms, coronawaves)


fatherss$geslacht<-"father" 
motherss$geslacht<-"mother" 

fatherss$inidvidualID<-paste("V",fatherss$ID, sep="")
motherss$inidvidualID<-paste("M",motherss$ID, sep="")

parents<-rbind(fatherss, motherss)


parents$waver<-parents$wave
parents$waver[parents$wave=="first"]<-"1.first"
parents$waver[parents$wave=="corona"]<-"2.corona"
  table(parents$waver)

mmodelc0<-lmer(coersive~ (1|ID)+ (1|ID:inidvidualID), data=parents)


mmodelc1<-lmer(coersive~werkprive+privewerk+ waver+opleiding+ jongerzwoertje + geslacht+ (1|ID)+ (1|ID:inidvidualID), data=parents)
summary(mmodelc1)


mmodelc2<-lmer(coersive~werkprive*waver +privewerk*waver +opleiding+ jongerzwoertje + geslacht+ (1|ID)+ (1|ID:inidvidualID), data=parents)
summary(mmodelc2)

#mmodelc2<-lmer(coersive~werkprive*wave*geslacht+ privewerk*wave*geslacht +opleiding+ jongerzwoertje +(1|ID)+ (1|ID:inidvidualID), data=parents)
#summary(mmodelc2)

r.squaredGLMM(mmodelc1) 
r.squaredGLMM(mmodelc2)

```




###Parent child relationship quality
```{r}
wave1vs<-wave1v
coronawavevs<-coronawavev
motherss<-rbind(wave1vs, coronawavevs)

wave1ms<-wave1m
coronawaves<-coronawave
fatherss<-rbind(wave1ms, coronawaves)

fatherss$geslacht<-"father" 
motherss$geslacht<-"mother" 

fatherss$inidvidualID<-paste("V",fatherss$ID, sep="")
motherss$inidvidualID<-paste("M",motherss$ID, sep="")

parents<-rbind(fatherss, motherss)


parents$waver<-parents$wave
parents$waver[parents$wave=="first"]<-"1.first"
parents$waver[parents$wave=="corona"]<-"2.corona"
  table(parents$waver)

mmodelr0<-lmer(relation~(1|ID)+ (1|ID:inidvidualID), data=parents)

mmodelr1<-lmer(relation~werkprive+privewerk +waver+opleiding+ jongerzwoertje +geslacht+ (1|ID)+ (1|ID:inidvidualID), data=parents)
summary(mmodelr1)

mmodelr2<-lmer(relation~werkprive*waver+privewerk*waver +opleiding+ jongerzwoertje +geslacht+(1|ID)+ (1|ID:inidvidualID), data=parents)
summary(mmodelr2)

#mmodelr2<-lmer(relation~werkprive*wave*geslacht +privewerk*wave*geslacht +opleiding+ jongerzwoertje +(1|ID)+ (1|ID:inidvidualID), data=parents)
#summary(mmodelr2)

r.squaredGLMM(mmodelr1) 
r.squaredGLMM(mmodelr2)
```


###########################################
######this were the main models above 
####below are extra checks for groups seperately 
##for men and women seperately
##by wave, with and withour outliers etcetera 


###################################################################################################################################################################

##First sep fatehrs and mothers


##wave 1 mothers
```{r}
regress<-lm(parchildrelation_m_M~privewerk_moeder+ werkprive_moeder+ opleidummymoeder +
              jongerzwoertje , data=corona)
summary(regress)

regress<-lm(coerciveparenting_m_M~privewerk_moeder+ werkprive_moeder+ opleidummymoeder +
              jongerzwoertje , data=corona)
summary(regress)

regress<-lm(positiveEncouragement_m_M~privewerk_moeder+ werkprive_moeder+ opleidummymoeder +
              jongerzwoertje , data=corona)
summary(regress)

```


#wave 2 mothers
```{r}
regress<-lm(parchildrel_corona_m_M~privewerk_moeder_corona+ werkprive_moeder_corona+ opleidummymoeder +
              jongerzwoertje_corona , data=corona)
summary(regress)

regress<-lm(coercive_corona_m_M~privewerk_moeder_corona+ werkprive_moeder_corona+ opleidummymoeder +
              jongerzwoertje_corona , data=corona)
summary(regress)

regress<-lm(posencourage_corona_m_M~privewerk_moeder_corona+ werkprive_moeder_corona+ opleidummymoeder +
              jongerzwoertje_corona , data=corona)
summary(regress)

#regress<-lm(consistency_corona_m_M~privewerk_moeder_corona+ werkprive_moeder_corona+ opleidummymoeder +
#              jongerzwoertje_corona , data=corona)
#summary(regress)
```



###wave 1 fathers
```{r}
regress<-lm(parchildrelation_m_V~privewerk_vader+ werkprive_vader+ opleidummyvader +
              jongerzwoertje , data=corona)
summary(regress)

regress<-lm(coerciveparenting_m_V~privewerk_vader+ werkprive_vader+ opleidummyvader +
              jongerzwoertje , data=corona)
summary(regress)

regress<-lm(positiveEncouragement_m_V~privewerk_vader+ werkprive_vader+ opleidummyvader +
              jongerzwoertje , data=corona)
summary(regress)

```



###wave 2 fathers
```{r}
regress<-lm(parchildrel_corona_m_V~privewerk_vader_corona+ werkprive_vader_corona+ opleidummyvader +
              jongerzwoertje_corona , data=corona)
summary(regress)

regress<-lm(coercive_corona_m_V~privewerk_vader_corona+ werkprive_vader_corona+ opleidummyvader +
              jongerzwoertje_corona , data=corona)
summary(regress)

regress<-lm(posencourage_corona_m_V~privewerk_vader_corona+ werkprive_vader_corona+ opleidummyvader +
              jongerzwoertje_corona , data=corona)
summary(regress)

#regress<-lm(consistency_corona_m_V~privewerk_vader_corona+ werkprive_vader_corona+ opleidummyvader +
#              jongerzwoertje_corona , data=corona)
#summary(regress)


```


###################################################################################################################################################################
##Step 4, regression models

###################################################################################################################################################################
##Step 4, without outliers


##mothers
```{r}
coronas<-corona[-c( 4, 79,92,56 ),]
regress<-lm(parchildrelation_m_M~privewerk_moeder+ werkprive_moeder+ opleidummymoeder +
              jongerzwoertje , data=coronas)
summary(regress)

coronas<-corona[-c(20 ,6 , 70, 56),]
regress<-lm(coerciveparenting_m_M~privewerk_moeder+ werkprive_moeder+ opleidummymoeder +
              jongerzwoertje , data=coronas)
summary(regress)

coronas<-corona[-c( 34,74 , 77, 16, 56, 57),]
regress<-lm(positiveEncouragement_m_M~privewerk_moeder+ werkprive_moeder+ opleidummymoeder +
              jongerzwoertje , data=coronas)
summary(regress)

```


#mothers wave 2
```{r}
coronas<-corona[-c( 92, 64, 90 ),]
regress<-lm(parchildrel_corona_m_M~privewerk_moeder_corona+ werkprive_moeder_corona+ opleidummymoeder +
              jongerzwoertje_corona , data=coronas)
summary(regress)

coronas<-corona[-c( 90,20 ),]
regress<-lm(coercive_corona_m_M~privewerk_moeder_corona+ werkprive_moeder_corona+ opleidummymoeder +
              jongerzwoertje_corona , data=coronas)
summary(regress)

coronas<-corona[-c(13),]
regress<-lm(posencourage_corona_m_M~privewerk_moeder_corona+ werkprive_moeder_corona+ opleidummymoeder +
              jongerzwoertje_corona , data=coronas)
summary(regress)


```



###fathers
```{r}
coronas<-corona[-c( 21, 10, 91, 7, 71),]
regress<-lm(parchildrelation_m_V~privewerk_vader+ werkprive_vader+ opleidummyvader +
             jongerzwoertje , data=coronas)
summary(regress)

coronas<-corona[-c( 17,71 ,82 ),]
regress<-lm(coerciveparenting_m_V~privewerk_vader+ werkprive_vader+ opleidummyvader +
              jongerzwoertje , data=coronas)
summary(regress)

coronas<-corona[-c( 21, 80, 71),]
regress<-lm(positiveEncouragement_m_V~privewerk_vader+ werkprive_vader+ opleidummyvader +
              jongerzwoertje , data=coronas)
summary(regress)

```



###fatehrs wave 2
```{r}
coronas<-corona[-c( 89,80 ,57, 17, 7, 54),]
regress<-lm(parchildrel_corona_m_V~privewerk_vader_corona+ werkprive_vader_corona+ opleidummyvader +
              jongerzwoertje_corona , data=coronas)
summary(regress)

coronas<-corona[-c(96,80 , 17, 54),]
regress<-lm(coercive_corona_m_V~privewerk_vader_corona+ werkprive_vader_corona+ opleidummyvader +
              jongerzwoertje_corona , data=coronas)
summary(regress)

coronas<-corona[-c( 89,80 ,82 ,93 , 54),]
regress<-lm(posencourage_corona_m_V~privewerk_vader_corona+ werkprive_vader_corona+ opleidummyvader +
              jongerzwoertje_corona , data=coronas)
summary(regress)


```


```{r}
##VIF and correlation between two types of conflict

cor.test(corona$werkprive_moeder, corona$privewerk_moeder)
cor.test(corona$werkprive_vader, corona$privewerk_vader)
cor.test(corona$werkprive_moeder_corona, corona$privewerk_moeder_corona)
cor.test(corona$werkprive_vader_corona, corona$privewerk_vader_corona)

```

###################################################################################################################################################################
##Step 3, regression models##

##With outliers winsorized 

```{r}
#install.packages("DescTools")
#library(DescTools)

corona$positiveEncouragement_m_M_W<-corona$positiveEncouragement_m_M; corona$positiveEncouragement_m_M_W<-DescTools::Winsorize(corona$positiveEncouragement_m_M_W, minval=2.25 , na.rm=T)
corona$positiveEncouragement_m_V_W<-corona$positiveEncouragement_m_V; corona$positiveEncouragement_m_V_W<-DescTools::Winsorize(corona$positiveEncouragement_m_V_W, minval=2.25 , na.rm=T)

corona$posencourage_corona_m_M_W<-corona$posencourage_corona_m_M; corona$posencourage_corona_m_M_W<-DescTools::Winsorize(corona$posencourage_corona_m_M_W, minval=2.25, na.rm=T)
corona$posencourage_corona_m_V_W<-corona$posencourage_corona_m_V; corona$posencourage_corona_m_V_W<-DescTools::Winsorize(corona$posencourage_corona_m_V_W, minval=2.25, na.rm=T)

corona$coerciveparenting_m_M_W<-corona$coerciveparenting_m_M; corona$coerciveparenting_m_M_W<-DescTools::Winsorize(corona$coerciveparenting_m_M_W, maxval=2.25, na.rm=T)
corona$coercive_corona_m_M_W<-corona$coercive_corona_m_M; corona$coercive_corona_m_M_W<-DescTools::Winsorize(corona$coercive_corona_m_M_W, maxval=2.25, na.rm=T)

corona$coerciveparenting_m_V_W<-corona$coerciveparenting_m_V; corona$coerciveparenting_m_V_W<-DescTools::Winsorize(corona$coerciveparenting_m_V_W, maxval=2.25, na.rm=T)
corona$coercive_corona_m_V_W<-corona$coercive_corona_m_V; corona$coercive_corona_m_V_W<-DescTools::Winsorize(corona$coercive_corona_m_V_W, maxval=2.25, na.rm=T)

corona$parchildrelation_m_M_W<-corona$parchildrelation_m_M; corona$parchildrelation_m_M_W<-DescTools::Winsorize(corona$parchildrelation_m_M_W, minval=3.25, na.rm=T)
corona$parchildrel_corona_m_M_W<-corona$parchildrel_corona_m_M; corona$parchildrel_corona_m_M_W<-DescTools::Winsorize(corona$parchildrel_corona_m_M_W, minval=3.25, na.rm=T)

corona$parchildrelation_m_V_W<-corona$parchildrelation_m_V; corona$parchildrelation_m_V_W<-DescTools::Winsorize(corona$parchildrelation_m_V_W, minval=3.25, na.rm=T)
corona$parchildrel_corona_m_V_W<-corona$parchildrel_corona_m_V; corona$parchildrel_corona_m_V_W<-DescTools::Winsorize(corona$parchildrel_corona_m_V_W, minval=3.25, na.rm=T)

###see what happens with a scatterplot
plot(corona$parchildrelation_m_M_W, corona$parchildrelation_m_M)

```
```{r}

```


##Voor corona voor moeders
```{r}
regress<-lm(parchildrelation_m_M_W~privewerk_moeder+ werkprive_moeder+ opleidummymoeder +
              jongerzwoertje , data=corona)
summary(regress)

regress<-lm(coerciveparenting_m_M_W~privewerk_moeder+ werkprive_moeder+ opleidummymoeder +
              jongerzwoertje , data=corona)
summary(regress)

regress<-lm(positiveEncouragement_m_M_W~privewerk_moeder+ werkprive_moeder+ opleidummymoeder +
              jongerzwoertje , data=corona)
summary(regress)

```


#tijdens corona voor moeders
```{r}
regress<-lm(parchildrel_corona_m_M_W~privewerk_moeder_corona+ werkprive_moeder_corona+ opleidummymoeder +
              jongerzwoertje_corona , data=corona)
summary(regress)

regress<-lm(coercive_corona_m_M_W~privewerk_moeder_corona+ werkprive_moeder_corona+ opleidummymoeder +
              jongerzwoertje_corona , data=corona)
summary(regress)

regress<-lm(posencourage_corona_m_M_W~privewerk_moeder_corona+ werkprive_moeder_corona+ opleidummymoeder +
              jongerzwoertje_corona , data=corona)
summary(regress)

#regress<-lm(consistency_corona_m_M~privewerk_moeder_corona+ werkprive_moeder_corona+ opleidummymoeder +
#              jongerzwoertje_corona , data=corona)
#summary(regress)
```



###Voor corona voor vaders
```{r}
regress<-lm(parchildrelation_m_V_W~privewerk_vader+ werkprive_vader+ opleidummyvader +
              jongerzwoertje , data=corona)
summary(regress)

regress<-lm(coerciveparenting_m_V_W~privewerk_vader+ werkprive_vader+ opleidummyvader +
              jongerzwoertje , data=corona)
summary(regress)

regress<-lm(positiveEncouragement_m_V_W~privewerk_vader+ werkprive_vader+ opleidummyvader +
              jongerzwoertje , data=corona)
summary(regress)

```



###Tijdens corona  voor vaders
```{r}
regress<-lm(parchildrel_corona_m_V_W~privewerk_vader_corona+ werkprive_vader_corona+ opleidummyvader +
              jongerzwoertje_corona , data=corona)
summary(regress)

regress<-lm(coercive_corona_m_V_W~privewerk_vader_corona+ werkprive_vader_corona+ opleidummyvader +
              jongerzwoertje_corona , data=corona)
summary(regress)

regress<-lm(posencourage_corona_m_V_W~privewerk_vader_corona+ werkprive_vader_corona+ opleidummyvader +
              jongerzwoertje_corona , data=corona)
summary(regress)

#regress<-lm(consistency_corona_m_V~privewerk_vader_corona+ werkprive_vader_corona+ opleidummyvader +
#              jongerzwoertje_corona , data=corona)
#summary(regress)


```

############################################################################################
##Step 5, hurdle model for difference between 4 and less, and within the less group 

```{r}
corona$binrela_m[corona$parchildrelation_m_M==4]<-1;  corona$binrela_m[corona$parchildrelation_m_M<4]<-0; table(corona$binrela_m)
corona$cutrela_m<-corona$parchildrelation_m_M; corona$cutrela_m[corona$parchildrelation_m_M==4]<-NA

corona$binrela_corona_m[corona$parchildrel_corona_m_M==4]<-1;  corona$binrela_corona_m[corona$parchildrel_corona_m_M<4]<-0; table(corona$binrela_corona_m)
corona$cutrela_corona_m<-corona$parchildrel_corona_m_M; corona$cutrela_corona_m[corona$parchildrel_corona_m_M==4]<-NA

corona$binrela_v[corona$parchildrelation_m_V==4]<-1;  corona$binrela_v[corona$parchildrelation_m_V<4]<-0; table(corona$binrela_v)
corona$cutrela_v<-corona$parchildrelation_m_V; corona$cutrela_v[corona$parchildrelation_m_V==4]<-NA

corona$binrela_corona_v[corona$parchildrel_corona_m_V==4]<-1;  corona$binrela_corona_v[corona$parchildrel_corona_m_V<4]<-0; table(corona$binrela_corona_v)
corona$cutrela_corona_v<-corona$parchildrel_corona_m_V; corona$cutrela_corona_v[corona$parchildrel_corona_m_V==4]<-NA

```

###For the binary outcome, less had to be removed because of outliers do not matter here in par-child rela 
```{r}
coronas<-corona[-c( 4, 56 ),] #79,92
regress<-glm(binrela_m~privewerk_moeder+ werkprive_moeder+ opleidummymoeder +
              jongerzwoertje , binomial, data=coronas)
summary(regress)
        
coronas<-corona  #[-c( 92, 64, 90 ),]
regress<-glm(binrela_corona_m~privewerk_moeder_corona+ werkprive_moeder_corona+ opleidummymoeder +
              jongerzwoertje_corona , binomial, data=coronas)
summary(regress)   

coronas<-corona[-c( 21, 71),]# , 10, 91, 7
regress<-glm(binrela_v~privewerk_vader+ werkprive_vader+ opleidummyvader +
              jongerzwoertje , binomial, data=coronas)
summary(regress)

coronas<-corona[-c( 89,80 , 54),]# ,17,57, 17, 7
regress<-glm(binrela_corona_v~privewerk_vader_corona+ werkprive_vader_corona+ opleidummyvader +
              jongerzwoertje_corona , binomial, data=coronas)
summary(regress)
```


##For the outliers removed
```{r}
coronas<-corona[-c( 4, 79,92,56 ),]
regress<-lm(cutrela_m~privewerk_moeder+ werkprive_moeder+ opleidummymoeder +
              jongerzwoertje , data=coronas)
summary(regress)
        
coronas<-corona[-c( 92, 64, 90 ),]
regress<-lm(cutrela_corona_m~privewerk_moeder_corona+ werkprive_moeder_corona+ opleidummymoeder +
              jongerzwoertje_corona , data=coronas)
summary(regress)   

coronas<-corona[-c( 21, 10, 91, 7, 71),]
regress<-lm(cutrela_v~privewerk_vader+ werkprive_vader+ opleidummyvader +
              jongerzwoertje , data=coronas)
summary(regress)

coronas<-corona[-c( 89,80 ,17,57, 17, 7, 54),]
regress<-lm(cutrela_corona_v~privewerk_vader_corona+ werkprive_vader_corona+ opleidummyvader +
              jongerzwoertje_corona , data=coronas)
summary(regress)
```


####Step 6, multilevel model for difference between waves in the relationship WFC and parenting
#Multilevel model
```{r}
setwd("C:/users/Renske/OneDrive - Erasmus University Rotterdam/Documents/3 hoek")
load("corona.RData")

installed.packages("ggplot2")
library(ggplot2)

options(max.print=1000000)
#names(corona)

install.packages("lme4")
library(lme4)
```



##Women models




##Significant effect of privewerk on coersive parenting, no interaction with wave
```{r}
wave1ms<-wave1m[-c(20 ,6 , 70, 56 ),]
coronawaves<-coronawave[-c( 90,20 ),]
motherss<-rbind(wave1ms, coronawaves)

mmodel<-lmer(coersive~werkprive+privewerk +opleiding+ jongerzwoertje+ wave +(1|ID), data=motherss)
summary(mmodel)

mmodel<-lmer(coersive~werkprive*wave+privewerk*wave +opleiding+ jongerzwoertje +(1|ID), data=motherss)
summary(mmodel)


```

##NO effect
```{r}
wave1ms<-wave1m[-c( 34,74 , 77, 16, 56, 57 ),]
coronawaves<-coronawave[-c( 13 ),]
motherss<-rbind(wave1ms, coronawaves)


mmodel<-lmer(encourage~werkprive+privewerk +opleiding+ jongerzwoertje+wave +(1|ID), data=motherss)
summary(mmodel)

mmodel<-lmer(encourage~werkprive*wave+privewerk*wave +opleiding+ jongerzwoertje +(1|ID), data=motherss)
summary(mmodel)

```

##no effect
```{r}
wave1ms<-wave1m[-c( 4, 79,92,56  ),]
coronawaves<-coronawave[-c( 92, 64, 90),]
motherss<-rbind(wave1ms, coronawaves)

mmodel<-lmer(relation~werkprive+privewerk +opleiding+ jongerzwoertje+ wave +(1|ID), data=mothers)
summary(mmodel)

mmodel<-lmer(relation~werkprive*wave+privewerk*wave +opleiding+ jongerzwoertje +(1|ID), data=mothers)
summary(mmodel)

```



#####VADERS##############




##NO effect, and no interaction with wave
```{r}
wave1vs<-wave1v[-c(17,71 ,82 ),]
coronawavevs<-coronawavev[-c(96,80 , 17, 54),]
fatherss<-rbind(wave1vs, coronawavevs)


mmodel<-lmer(coersive~werkprive+privewerk +opleiding+ jongerzwoertje+wave +(1|ID), data=fathers)
summary(mmodel)

mmodel<-lmer(coersive~werkprive*wave+privewerk*wave +opleiding+ jongerzwoertje +(1|ID), data=fathers)
summary(mmodel)

```

##NO effect
```{r}
wave1vs<-wave1v[-c(21, 80, 71 ),]
coronawavevs<-coronawavev[-c(89,80 ,82 ,93 , 54),]
fatherss<-rbind(wave1vs, coronawavevs)

mmodel<-lmer(encourage~werkprive+privewerk +opleiding+ jongerzwoertje+wave +(1|ID), data=fathers)
summary(mmodel)

mmodel<-lmer(encourage~werkprive*wave+privewerk*wave +opleiding+ jongerzwoertje +(1|ID), data=fathers)
summary(mmodel)
```

##significant effect and interaction with wave. 
```{r}
wave1vs<-wave1v[-c( 21, 10, 91, 7, 71),]
coronawavevs<-coronawavev[-c(89,80 ,57, 17, 7, 54),]
fatherss<-rbind(wave1vs, coronawavevs)

mmodel<-lmer(relation~werkprive+privewerk +opleiding+ jongerzwoertje+wave +(1|ID), data=fathers)
summary(mmodel)

mmodel<-lmer(relation~werkprive*wave+privewerk*wave +opleiding+ jongerzwoertje +(1|ID), data=fathers)
summary(mmodel)
```
