---
title: "R Notebook"
output: html_notebook
---

```{r}
rm(list=ls())

setwd("C:/users/renske/OneDrive - Erasmus University Rotterdam/Documents/3 hoek")
load("corona.RData")

install.packages("ggplot2")
library(ggplot2)

options(max.print=1000000)
#names(corona)

install.packages("Rmisc")
library(Rmisc)

install.packages("lme4")
library(lme4)

library(data.table)
library(tidyverse)
```



##remove WFC if this is missing in one of the waves
```{r}
corona$werkprive_moederm<-corona$werkprive_moeder; corona$werkprive_moederm[is.na(corona$werkprive_moeder_corona)]<-NA
corona$werkprive_moeder_coronam<-corona$werkprive_moeder_corona;corona$werkprive_moeder_coronam[is.na(corona$werkprive_moeder)]<-NA

corona$werkprive_vaderm<-corona$werkprive_vader; corona$werkprive_vaderm[is.na(corona$werkprive_vader_corona)]<-NA
corona$werkprive_vader_coronam<-corona$werkprive_vader_corona;corona$werkprive_vader_coronam[is.na(corona$werkprive_vader)]<-NA

```

```{r}
corona$privewerk_moederm<-corona$privewerk_moeder; corona$privewerk_moederm[is.na(corona$privewerk_moeder_corona)]<-NA
corona$privewerk_moeder_coronam<-corona$privewerk_moeder_corona;corona$privewerk_moeder_coronam[is.na(corona$privewerk_moeder)]<-NA

corona$privewerk_vaderm<-corona$privewerk_vader; corona$privewerk_vaderm[is.na(corona$privewerk_vader_corona)]<-NA
corona$privewerk_vader_coronam<-corona$privewerk_vader_corona;corona$privewerk_vader_coronam[is.na(corona$privewerk_vader)]<-NA


```



##measures of parenting during both waves. 
##remove this if WFC is missing in one of the two waves

```{r}
corona$missing_M<-"no"
corona$missing_M[is.na(corona$werkprive_moeder)]<-"missing"
corona$missing_M[is.na(corona$werkprive_moeder_corona)]<-"missing"
table(corona$missing_M)

corona$missing_V<-"no"
corona$missing_V[is.na(corona$werkprive_vader)]<-"missing"
corona$missing_V[is.na(corona$werkprive_vader_corona)]<-"missing"
table(corona$missing_V)



corona$positiveEncouragement_m_M<-corona$positiveEncouragement_M; corona$positiveEncouragement_M[corona$missing_M=="missing"]<-NA
corona$positiveEncouragement_m_V<-corona$positiveEncouragement_V; corona$positiveEncouragement_m_V[corona$missing_V=="missing"]<-NA
corona$posencourage_corona_m_M<-corona$posencourage_corona_M; corona$posencourage_corona_m_M[corona$missing_M=="missing"]<-NA
corona$posencourage_corona_m_V<-corona$posencourage_corona_V; corona$posencourage_corona_m_V[corona$missing_V=="missing"]<-NA
corona$coerciveparenting_m_M<-corona$coerciveparenting_M; corona$coerciveparenting_m_M[corona$missing_M=="missing"]<-NA
corona$coercive_corona_m_M<-corona$coercive_corona_M; corona$coercive_corona_m_M[corona$missing_M=="missing"]<-NA
corona$coerciveparenting_m_V<-corona$coerciveparenting_V; corona$coerciveparenting_m_V[corona$missing_V=="missing"]<-NA
corona$coercive_corona_m_V<-corona$coercive_corona_V; corona$coercive_corona_m_V[corona$missing_V=="missing"]<-NA
corona$parchildrelation_m_M<-corona$parchildrelation_M; corona$parchildrelation_m_M[corona$missing_M=="missing"]<-NA
corona$parchildrel_corona_m_M<-corona$parchildrel_corona_M; corona$parchildrel_corona_m_M[corona$missing_M=="missing"]<-NA
corona$parchildrelation_m_V<-corona$parchildrelation_V; corona$parchildrelation_m_V[corona$missing_V=="missing"]<-NA
corona$parchildrel_corona_m_V<-corona$parchildrel_corona_V; corona$parchildrel_corona_m_V[corona$missing_V=="missing"]<-NA

```

##dataset for men
```{r}
men<- corona[c("Nr_G","werkprive_vaderm", "werkprive_vader_coronam", "opleidummyvader", "privewerk_vaderm", "privewerk_vader_coronam", "increase_privewerk_vader", "increase_werkprive_vader", "geboorte", "Werk_uren_compleet_V", "werkurenvader_corona","increase_werkuren_vader", "Werk_uren_compleet_M", "werkurenmoeder_corona","increase_werkuren_moeder","huisvader_corona", "huismoeder_corona", "startstopworking_vader", "startstopworking_moeder","noodopvangbeschikbaar_V", "schoolwerk_uren_vader_corona", "increase_relativeinv_V", "werkurenvader_corona_cats", "werkurenmoeder_corona_cats", "increase_werkuren_vader_imputed", "increase_werkuren_moeder_imputed")]
men$geslacht<-"man"
head(men)
```

#change labels
```{r}
library(data.table)
setnames(men, old = c("Nr_G","werkprive_vaderm", "werkprive_vader_coronam", "opleidummyvader", "privewerk_vaderm", "privewerk_vader_coronam", "increase_privewerk_vader", "increase_werkprive_vader", "geboorte", "Werk_uren_compleet_V", "werkurenvader_corona","increase_werkuren_vader", "Werk_uren_compleet_M", "werkurenmoeder_corona","increase_werkuren_moeder","huisvader_corona", "huismoeder_corona", "startstopworking_vader", "startstopworking_moeder","noodopvangbeschikbaar_V", "schoolwerk_uren_vader_corona", "increase_relativeinv_V", "werkurenvader_corona_cats", "werkurenmoeder_corona_cats", "increase_werkuren_vader_imputed", "increase_werkuren_moeder_imputed", "geslacht"), 
         new = c("Nr_G",
                   "werkprive", "werkprive_corona", "opleidummy","privewerk" ,"privewerk_corona"  ,"increase_privewerk",  "increase_werkprive" , "geboorte", "werkuren", "werkuren_corona", "increase_werkuren","werkuren_partner", "werkuren_corona_partner", "increase_werkuren_partner","inactive_corona", "inactive_partner_corona", "startstopworking", "startstopworking_partner","noodopvangbeschikbaar", "schoolwerk_uren_corona", "increase_relativeinv", "werkuren_corona_cats", "werkurenpartner_corona_cats", "increase_werkuren_imputed", "increase_werkuren_partner_imputed", "geslacht" ))


head(men)
```


#for mothers
```{r}
women<- corona[c("Nr_G","werkprive_moederm", "werkprive_moeder_coronam", "opleidummymoeder", "privewerk_moederm", "privewerk_moeder_coronam", "increase_privewerk_moeder", "increase_werkprive_moeder", "geboorte", "Werk_uren_compleet_M", "werkurenmoeder_corona","increase_werkuren_moeder", "Werk_uren_compleet_V", "werkurenvader_corona","increase_werkuren_vader", "huismoeder_corona","huisvader_corona", "startstopworking_moeder", "startstopworking_vader","noodopvangbeschikbaar_M", "schoolwerk_uren_vader_corona", "increase_relativeinv_M", "werkurenmoeder_corona_cats", "werkurenvader_corona_cats", "increase_werkuren_moeder_imputed", "increase_werkuren_vader_imputed")]
women$geslacht<-"woman"
head(women)
```

#change labels
```{r}
library(data.table)
setnames(women, old = c("Nr_G","werkprive_moederm", "werkprive_moeder_coronam", "opleidummymoeder", "privewerk_moederm", "privewerk_moeder_coronam", "increase_privewerk_moeder", "increase_werkprive_moeder", "geboorte", "Werk_uren_compleet_M", "werkurenmoeder_corona","increase_werkuren_moeder", "Werk_uren_compleet_V", "werkurenvader_corona","increase_werkuren_vader", "huismoeder_corona","huisvader_corona", "startstopworking_moeder", "startstopworking_vader","noodopvangbeschikbaar_M", "schoolwerk_uren_vader_corona", "increase_relativeinv_M", "werkurenmoeder_corona_cats", "werkurenvader_corona_cats", "increase_werkuren_moeder_imputed", "increase_werkuren_vader_imputed", "geslacht" ), 
         new = c("Nr_G",
                   "werkprive", "werkprive_corona", "opleidummy","privewerk" ,"privewerk_corona"  ,"increase_privewerk",  "increase_werkprive" , "geboorte","werkuren", "werkuren_corona", "increase_werkuren","werkuren_partner", "werkuren_corona_partner", "increase_werkuren_partner","inactive_corona", "inactive_partner_corona", "startstopworking", "startstopworking_partner","noodopvangbeschikbaar", "schoolwerk_uren_corona", "increase_relativeinv", "werkuren_corona_cats", "werkurenpartner_corona_cats", "increase_werkuren_imputed", "increase_werkuren_partner_imputed", "geslacht"))

head(women)
```



##Merge the two dataframes below eachother
#the ID we can use later for specifying the family level
```{r}
coronalong<-rbind(men, women)


#Create category:
coronalong$category<-NA
coronalong$category[coronalong$opleidummy==0 & coronalong$geslacht=="man"]<-"4.lowman"
coronalong$category[coronalong$opleidummy==1 & coronalong$geslacht=="man"]<-"3.highmenman"
coronalong$category[coronalong$opleidummy==0 & coronalong$geslacht=="woman"]<-"2.lowwoman"
coronalong$category[coronalong$opleidummy==1 & coronalong$geslacht=="woman"]<-"1.highwoman"

coronalong$geslachtbin<-NA
coronalong$geslachtbin[coronalong$geslacht=="man"]<-1
coronalong$geslachtbin[coronalong$geslacht=="woman"]<-0

coronalong$opleidummybin<-NA
coronalong$opleidummybin[coronalong$opleidummy==0]<-1
coronalong$opleidummybin[coronalong$opleidummy==1]<-0


setwd("C:/users/renske/OneDrive - Erasmus University Rotterdam/Documents/3 hoek")
save(coronalong, file = "coronalong.RData")
```


```{r}
#rm(list=ls())

#install.packages("lme4")
library(lme4)

setwd("C:/users/renske/OneDrive - Erasmus University Rotterdam/Documents/3 hoek")
load("coronalong.RData")


head(coronalong)
```



##Simple tests
##WFconflict and increase conflict by education
```{r}
tapply(coronalong$privewerk, coronalong$opleidummy,mean, na.rm=T)
tapply(coronalong$privewerk_corona, coronalong$opleidummy, mean,na.rm=T)


tapply(coronalong$increase_privewerk, coronalong$opleidummy, mean, na.rm=T)
t.test(coronalong$increase_privewerk~coronalong$opleidummy)
```
#WFconflcit and increase by education
```{r}

tapply(coronalong$werkprive, coronalong$opleidummy, mean, na.rm=T)
tapply(coronalong$werkprive_corona, coronalong$opleidummy, mean,na.rm=T)

tapply(coronalong$increase_werkprive, coronalong$opleidummy, mean, na.rm=T)
t.test(coronalong$increase_werkprive~coronalong$opleidummy)
```
##increase significant for high vs lower educated
```{r}
coronalonglaag<-subset(coronalong, opleidummy==0)
coronalonghoog<-subset(coronalong, opleidummy==1)

t.test(coronalonghoog$werkprive,coronalonghoog$werkprive_corona)

t.test(coronalonglaag$werkprive,coronalonglaag$werkprive_corona)


t.test(coronalonghoog$privewerk,coronalonghoog$privewerk_corona)

t.test(coronalonglaag$privewerk,coronalonglaag$privewerk_corona)

```
##Increase different for the four groups? 
```{r}

#anova<-(lm(increase_privewerk~category+geboorte, data=coronalong))
#summary(anova)
mmodel0<-lmer(increase_privewerk~(1|Nr_G), data=coronalong)
summary(mmodel0)


##nu met imputed werkuren:
mmodel1b<-lmer(increase_privewerk~opleidummybin+ geslachtbin +geboorte +increase_werkuren_imputed + increase_werkuren_partner_imputed+ (1|Nr_G), data=coronalong)
summary(mmodel1b)


#mmodel<-lmer(increase_privewerk~category+geboorte +(1|Nr_G), data=coronalong)
#summary(mmodel)
```
```{r}
#anova<-(lm(increase_werkprive~category+geboorte, data=coronalong))
#summary(anova)
mmodel00<-lmer(increase_werkprive~(1|Nr_G), data=coronalong)
summary(mmodel00)

##met imputed werkuren
mmodel11b<-lmer(increase_werkprive~opleidummybin+ geslachtbin +geboorte +increase_werkuren_imputed + increase_werkuren_partner_imputed+(1|Nr_G), data=coronalong)
summary(mmodel11b)


```

###R2 of these multilevel models 
```{r}

#privewerk
1-logLik(mmodel1)/logLik(mmodel0)

#werkprive
1-logLik(mmodel11)/logLik(mmodel00)
```

##Extra controls


##Increase different for the four groups? 
```{r}
#anova<-(lm(increase_privewerk~category+geboorte, data=coronalong))
#summary(anova)
mmodel0<-lmer(increase_privewerk~(1|Nr_G), data=coronalong)
summary(mmodel0)



mmodel3<-lmer(increase_privewerk~opleidummybin+ geslachtbin +geboorte+increase_werkuren+ increase_werkuren_partner +noodopvangbeschikbaar+ (1|Nr_G), data=coronalong)
summary(mmodel3)

mmodel4<-lmer(increase_privewerk~opleidummybin+ geslachtbin +geboorte+increase_werkuren+ increase_werkuren_partner + increase_relativeinv+ (1|Nr_G), data=coronalong)
summary(mmodel4)




```

```{r}
#anova<-(lm(increase_werkprive~category+geboorte, data=coronalong))
#summary(anova)

mmodel00<-lmer(increase_werkprive~(1|Nr_G), data=coronalong)
summary(mmodel00)



mmodel33<-lmer(increase_werkprive~opleidummybin+ geslachtbin +geboorte +increase_werkuren+increase_werkuren_partner+noodopvangbeschikbaar+(1|Nr_G), data=coronalong)
summary(mmodel33)

mmodel44<-lmer(increase_werkprive~opleidummybin+ geslachtbin +geboorte +increase_werkuren+increase_werkuren_partner+increase_relativeinv+(1|Nr_G), data=coronalong)
summary(mmodel44)


```

```{r}

#3 is noodopvang
#4 is relative involvement 

#privewerk
1-logLik(mmodel3)/logLik(mmodel0)
1-logLik(mmodel4)/logLik(mmodel0)

#werkprive
1-logLik(mmodel33)/logLik(mmodel00)
1-logLik(mmodel44)/logLik(mmodel00)
```

